Titeln på avhandlingens språk

### 2022-08-22 model.tex
working

\begin{enumerate}
    \item System slow-down induces additional behavioral slow-down which scales with the decrease in system responsiveness.
    Moreover, users become progressively slower the longer they spend in a degraded system state.

@@

Using these insights, we design a generator of realistic execution times for step-based \ac{WCA}.
The generator further builds upon the original data collected for~\cite{olguinmunoz:impact2021}; this data is first preprocessed and then sampled according to a series of rules in order to produce novel,realistic sequences of execution times for a task.
Alternatively, instead of sampling directly from the preprocessed data, a theoretical distribution can be fitted, thus allowing for generation of realistic synthetic execution times.

>>>>

\begin{enumerate}
    \item System slow-down induces \emph{additional} behavioral slow-down which scales with the decrease in system responsiveness.
    Moreover, users become progressively slower the longer they spend in a degraded system state.

@@

Based on these insights and the data collected for~\cite{olguinmunoz:impact2021}, we design a generator of realistic execution times for step-based \ac{WCA}.

\todo[inline]{Diagram of model?}

\begin{algorithm}
    \caption{Timing model algorithm}
    \KwIn{%
        \begin{itemize}
            \item $T_\text{start}$: start timestamp of the previous step.
            \item $T_\text{success}$: capture timestamp of the succesful sample of the previous step.
            \item $T_\text{end}$: end timestamp of the previous step.
            \item $t_\text{exec}$: execution time (in seconds) of the previous step.
        \end{itemize}%
    }
    \KwOut{$t_\text{exec}'$: execution time for the current step.}

    \Comment{%
        Initial values:\\
        $d \leftarrow 0$\\
        $I_\text{prev} \leftarrow \text{NULL}$
    }
    $t_\text{wait} \leftarrow T_\text{success} - (T_\text{start} + t_\text{exec})$\;
    $t_\text{round-trip} \leftarrow T_\text{end} - T_\text{success}$\;
    $i \leftarrow t_\text{wait} + t_\text{round-trip}$ \Comment*[r]{raw impairment}
    $I \leftarrow \text{BIN}(i)$ \Comment*[r]{bin impairment into\\discrete levels}

    \If{$I_\text{prev} == \text{NULL}$}{%
        $d \leftarrow 1$\;
        $T \leftarrow \text{NO TRANSITION}$\;
    } \ElseIf{$I_\text{prev} < I$}{%
        $d \leftarrow 1$\;
        $T \leftarrow \text{LOWER TO HIGHER} $
    } \ElseIf{$I_\text{prev} > I$}{%
        $d \leftarrow 1$\;
        $T \leftarrow \text{HIGHER TO LOWER} $  
    }

\end{algorithm}

This data is first preprocessed and then sampled according to a series of rules in order to produce novel,realistic sequences of execution times for a task.
Alternatively, instead of sampling directly from the preprocessed data, a theoretical distribution can be fitted, thus allowing for generation of realistic synthetic execution times.
